\vspace{-2.0cm} \textbf{Talking with body expressions} \\ \Large \textbf{A method for detecting signs in a weakly annotated dataset}

### 2019-09-10 article/article-tesis.tex
adding a better audio transcription aggregation mechanism

\textbf{Bag of Words (BoW)} or \textbf{Bag of Visual Words (BoVW)} based on natural language processing techniques is one of the simplest and oldest local descriptor encoding strategies that counts the number of occurrences of a set of image features \cite{wang2019hallucinating}, when applied to Computer Vision is a technique used to create images representations or features vectors used that can be learned by CNNs, resulting on improved images classification and video classification. 

>>>>

\textbf{Bag of Words (BoW)} or \textbf{Bag of Visual Words (BoVW)} based on natural language processing techniques is one of the simplest and oldest local descriptor encoding strategies. In its simplest form, it consists of (i) clustering with k-means a collection of descriptor vectors from the training set to build so-called visual vocabulary, (ii) as signing each descriptor to its nearest cluster center from the visual dictionary, and (iii) aggregating the one-hot assignment vectors via average pooling \cite{wang2019hallucinating}, when applied to Computer Vision is a technique used to create images representations or features vectors used that can be learned by CNNs, resulting on improved images classification and video classification. 
